\documentclass[a4paper]{scrreprt}



\title{Dorbits}
\subtitle{Playermade Satellite Evolution}
\author{David Wyss}


\begin{document}
\maketitle

\tableofcontents

\section{Main Concept}
The core game-loop is to create other drones, which exploit other drones and collect resources. 
Examples
\begin{itemize}
	\item All drones are aggressive, wait and collect what's left.
	\item All drones are peacful, destroy them and loot  what's left.
	\item Enemy Player relies only on your surveillance which he hacked. Destroy your own drones at strategically important moments
\end{itemize}

\section{Player(s) / Target-group}
Ugur

\section{Genre}
Strategy Game.

\section{Art Style}
Background: Lots of void with stars and nebulae\\
Ingame Objects: Symple Generated Shaders\\
IRL Planets: Use NASAs High Res Pics\\
GUI: Minimalistic

\chapter{Gameplay and Game Setting}
Drones are programmed, they interact with each other and their environment

\section{Story}
who knows 2 programmers fighting tech-religous wars with drone factories stolen from their respective countrey? The Dorg Collective origins?


\section{World/Environment}
Depends. We could take a fictional version of Earth or something new. Whatever suits us best.

\section{Main Objective}
Variable Depending on Game Mode.
\begin{itemize}
    \item Destroy all things belonging to enemy player.
    \item Destroy all other drones 
\end{itemize}


\section{Core Mechanics}
Create and Program Drones. Exploit, Destroy and Manipulate other Drones. Collect Resources and gain a strategic edge.

\section{Controls}
\begin{itemize}
    \item Rebindable Keys
    \item Camera movement. hjkl
\end{itemize}


\chapter{Front End}
TODO

\section{Start Screen}

\section{Menus}

\section{End Screen}
\section{Controls}
\begin{itemize}
    \item Globe View [G]
    \item Drone View [G][Drone identifier]
    \item Create Drone View [C]
\end{itemize}


\chapter{Technology}
\section{Target Systems}
    Linux and TempleOS

\section{Hardware}
Relatively low, depends on the amount of Drones ingame desired.

\section{Development Systems/Tools}
\begin{itemize}
	\item Godot
	\item \LaTeX
	\item Gdscript
	\item Git
	\item Open Source Github Equivalent 
\end{itemize}


\chapter{Team and Credits}

\begin{itemize}
    \item David Wyss: Vize-Executive David
    \item David Bart: Executive David
\end{itemize}

\end{document}
